Pipit on the Post: Proving Pre- and Post-conditions of Reactive Systems

### 2024-01-17 2024pipit/section/40-Transition.tex
copy

\begin{theorem}[translation-abstraction]
  For a well-typed causal expression $e$ and streaming history $\Sigma$, if $e$ evaluates to $v$ $(\bigstep{\Sigma}{e}{v})$, then there exists a sequence of free heaps $\Sigma_{F}$ such that repeated application of the transition system's step results in $v$.
\end{theorem}

>>>>

\begin{theorem}[translation-abstraction]
  For a well-typed causal expression $e$ and streaming history $\Sigma$, if $e$ evaluates to stream $V$ $(\bigsteps{\Sigma}{e}{V})$, then there exists a sequence of free heaps $\Sigma_{F}$ such that repeated application of the transition system's step results in $V$.
\end{theorem}
